Online analysis supplement

### 2021-11-05 index.Rmd
analyses wip

---
title: "Online analysis supplement"
description: |
  A global study of adolescents’ digital technology adoption and its associations with well-being and mental health
author:
  - name: Matti Vuorre
    url: https://vuorre.netlify.app
    affiliation: Oxford Internet Institute
    affiliation_url: https://www.oii.ox.ac.uk/people/matti-vuorre/
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
    fig_width: 8
    fig_height: 6
    fig_retina: 2
    dev: "ragg_png"
    code_folding: true
---

@@

We downloaded the relevant data from sources to data-raw. We cannot share the data here but indicate below how and when each data table was obtained.

@@

```{r settings}
# Packages
library(readxl)
library(brms)
library(ragg)
library(scales)
library(ggh4x)
library(tidybayes)
library(naniar)
library(ggdist)
library(parameters)
library(countrycode)
library(multidplyr)
library(lme4)
library(emmeans)
library(plotly)
library(knitr)
library(patchwork)
library(bayestestR)
library(lubridate)
library(haven)
library(janitor)
library(broom)
library(kableExtra)
library(ggbeeswarm)
library(ggstance)
library(sysfonts)
library(tidyverse)

@@

# parallel computations
MAX_CORES <- parallel::detectCores(logical = TRUE) / 2
cluster <- new_cluster(MAX_CORES)
cluster_library(cluster, c("lme4", "dplyr", "stringr"))

@@

### ITU

@@

```{r}
# Read and reshape fixed broadband data
itu_fixed <- read_excel(
  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("Year", "Variable")) %>% 
  pivot_wider(names_from = Variable) %>% 
  mutate(value = as.numeric(value))

# Read and reshape mobile broadband data
itu_mobile <- read_excel(
  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("Year", "Variable")) %>% 
  pivot_wider(names_from = Variable) %>% 
  mutate(value = as.numeric(value))

# Percent using internet
itu_percent <- read_excel(
  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("Year", "Variable")) %>% 
  pivot_wider(names_from = Variable) %>% 
  mutate(value = as.numeric(value))

# Merge to one table in wide format (oldest on left to include all years)
itu <- left_join(
  select(itu_percent, Country, Year, Internet = value),
  select(itu_fixed, Country, Year, Fixed = value)
) %>% 
  left_join(
    select(itu_mobile, Country, Year, Mobile = value)
  ) %>% 
  mutate(across(-Country, as.numeric))

# values (1-100) to proportions (0-1)
itu <- itu %>% 
  mutate(across(c(Fixed, Mobile, Internet), function(x) x/100))

# Standardise country names
# This drops six small regions not recognised by countryname()
itu <- itu %>% 
  mutate(Country = countryname(Country)) %>% 
  drop_na(Country)

@@

Remove countries with no internet data

```{r}
itu_countries_missing <- itu %>% 
  group_by(Country) %>% 
  summarise(
    years = n(), 
    missing_fixed = sum(is.na(Fixed)),
    missing_mobile = sum(is.na(Mobile)),
    missing_internet = sum(is.na(Internet))
  ) %>% 
  filter(
    missing_fixed == years | 
      missing_mobile == years |
      missing_internet == years
  )
itu_countries_missing <- itu_countries_missing %>% 
  filter(
    missing_fixed==years & 
      missing_mobile==years & missing_internet==years
  ) %>% 
  select(Country)
itu <- anti_join(itu, itu_countries_missing)
```

Missing values

```{r}
# Calculate numbers of missing values for fixed (2004-) and mobile (2007-)
bind_rows(
  select(itu, Internet) %>% 
    miss_var_summary(),
  filter(itu, Year >= 2004) %>% 
    select(Fixed) %>% 
    miss_var_summary(),
  filter(itu, Year >= 2007) %>% 
    select(Mobile) %>% 
    miss_var_summary()
) %>% 
  mutate(pct_miss = percent(pct_miss/100)) %>% 
  kbl(caption = "ITU Missingness") %>% 
  kable_styling(full_width = FALSE)
```

Impute missing values. We first replace missing initial values with zeros, assuming that they were not logged because practically zero. Then proceed with linear interpolation from there.

```{r}
library(imputeTS)

itu <- itu %>% 
  group_by(Country) %>% 
  # If first value is missing, replace with zero
  mutate(
    i = 1:n(),
    across(
      c(Internet, Fixed, Mobile), 
      .fns = list(
        i = possibly(function(x) if_else(is.na(x) & i==1, 0, x), otherwise = NaN)
      )
    )
  ) %>% 
  # Linear interpolation
  mutate(
    across(
      c(Internet_i, Fixed_i, Mobile_i), 
      possibly(function(x) na_interpolation(x), otherwise = NaN)
    )
  ) %>% 
  # Remove variables before they existed
  mutate(
    Fixed_i = if_else(Year < 2004, NaN, Fixed_i),
    Mobile_i = if_else(Year < 2007, NaN, Mobile_i)
  ) %>% 
  # Remove unnecessary index variable
  select(-i) %>% 
  ungroup()

# Don't impute observations forward (unless they are zeroes in the beginning)
itu <- itu %>% 
  mutate(
    across(
      ends_with("_i"), 
      ~if_else(.x == lag(.x) & .x!=0, NaN, .x)
    )
  )

# Examine output
itu <- itu %>% 
  select(
    Country, Year, 
    starts_with("Internet"),
    starts_with("Fixed"),
    starts_with("Mobile")
  )
# itu %>% 
#   mutate(across(-c(Country, Year), ~percent(.x, .001))) %>% 
#   View

# Replace old variables with imputed
itu <- itu %>% 
  select(-c(Internet, Fixed, Mobile)) %>% 
  rename_with(~str_replace(.x, "_i", ""))
```

The Global Burden of Disease data CSVs were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02.

```{r gbd-data-clean}
# Load data files and merge to one table
# We need names and IDs because there are two Georgias
gbd <- list.files(
  "data-raw/GBD/gbd-2021-11-02/", 
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>% 
  read_csv()

# Cleaning

# prevalence (total number of cases)
# "Rate": Total cases per 100,000 population
# We convert this to a percentage
distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>% 
  mutate(across(c(val, upper, lower), ~.x/1000))

# Clean cause names
distinct(gbd, cause)
gbd <- gbd %>% 
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Self-harm"
    )
  )

# Harmonise names with other datasets and capitalize
gbd <- gbd %>% 
  rename(
    Country = location,
    Year = year,
    Sex = sex,
    Age = age,
    Cause = cause
  )

# Harmonise country names
# Check where new name doesn't match with proposed new name
# gbd %>%
#   distinct(Country) %>%
#   mutate(Country2 = countryname(Country)) %>%
#   filter(Country!=Country2 | is.na(Country2)) %>%
#   arrange(Country) %>%
#   View()
# Replace old with new standard name, drop where new name doesn't exist
gbd <- gbd %>% 
  mutate(Country = countryname(Country)) %>% 
  drop_na(Country)
```

### World bank

```{r}
wb <- read_csv(
  "data-raw/world-bank/population/API_SP.POP.TOTL_DS2_en_csv_v2_2163507.csv", 
  skip = 3
)
wb <- wb %>% 
  select(Country = `Country Name`, `2000`:`2019`) %>%
  pivot_longer(-Country, names_to = "Year", values_to = "Pop") %>% 
  mutate(Year = as.numeric(Year))

wb <- wb %>% 
  mutate(Country = countryname(Country)) %>% 
  drop_na(Country)
```

### GLOBE Regions

We group the countries into GLOBE regions.

```{r}
regions <- read_csv(
  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
) %>% 
  # Jebb et al used * to indicate deviance from GLOBE, remove
  mutate(Country = str_remove_all(Country, "\\*")) %>% 
  # Standardize country names
  # This drops Nagorno-Karabakh Republic
  mutate(Country = countryname(Country)) %>% 
  drop_na(Country)

distinct(itu, Country)
distinct(regions, Region)

# ITU countries not present in region data
filter(
  distinct(itu, Country), 
  !(Country %in% unique(regions$Country))
) %>% 
  arrange(Country) %>% 
  write_csv("data-raw/Regions/ITU-countries-without-region.csv")

# I then filled missing regions in Jebb et al and extended GLOBE referenced therein
regions <- read_csv(
  "data-raw/Regions/ITU-countries-without-region-filled.csv"
) %>% 
  select(Country, Region) %>% 
  bind_rows(regions) %>% 
  drop_na(Region)

# GBD countries not present in region data
filter(
  distinct(gbd, Country),
  !(Country %in% unique(regions$Country))
) %>% 
  arrange(Country) %>% 
  write_csv("data-raw/Regions/GBD-countries-without-region.csv")

# Load in above filled with regions

# Shorter name for plots
regions <- regions %>% 
  mutate(Region = if_else(Region=="Sub-Sahara Africa", "Africa", Region))

# Reorder labels
regions <- regions %>% 
  mutate(
    Region = factor(
      Region,
      levels = c(
        "Africa", "Latin America", "Anglo", "Arab", 
        "Confucian Asia", "Southern Asia", "Eastern Europe", 
        "Germanic Europe", "Latin Europe", "Nordic Europe"
      )
    )
  )

# Format labels to use line breaks instead of spaces
levels(regions$Region) <- str_replace_all(levels(regions$Region), " ", "\n")

# Remove duplicated countries
regions %>% 
  count(Country, sort = TRUE)
regions <- distinct(regions)

# We then use these regions
itu <- itu %>% 
  left_join(regions)
```

## Complete study dataset

We end up with a dataset that has predictors (internet access) at the level of country and year. Outcomes are also at the level of country and year, but additionally vary by sex and age group.

```{r}
# For models, we rescale year; centred at 2013 and one unit indicates 2007 to 2019
itu <- itu %>% 
  mutate(Time = (Year - 2013) / 12)

# Create predictor, lagged and centered on 2013
itu <- itu %>% 
  arrange(Country, Year) %>% 
  group_by(Country) %>% 
  mutate(Internet1 = lag(Internet, 1)) %>% 
  mutate(Internet1 = Internet1 - Internet1[Year==2013]) %>%
  ungroup()

# Merge data sets
d <- left_join(itu, gbd)

# What to do with countries with no outcomes--drop
d <- d %>% 
  drop_na(Cause)

# Contrast code sex
d$Sex <- factor(d$Sex)
contrasts(d$Sex) <- c(-.5, .5)
```

@@

```{r}
# Mean users in first and last year
itu %>% 
  filter(Year %in% c(2000, 2020)) %>% 
  group_by(Year) %>% 
  summarise(mean(Internet, na.rm = TRUE))
# Regions
itu %>% 
  filter(Year == 2020) %>% 
  group_by(Region, Year) %>% 
  summarise(m = mean(Internet, na.rm = TRUE)) %>% 
  arrange(m)
itu %>% drop_na(Internet) %>% {length(unique(.$Country))}
```

```{r}
# Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
p_itu <- itu %>% 
  mutate(Year = make_date(Year)) %>% 
  # Do something about countries with no region if they have outcome data
  drop_na(Region) %>% 
  pivot_longer(c(Fixed, Mobile, Internet), names_to = "Type") %>% 
  mutate(Type = factor(Type, levels = c("Internet", "Fixed", "Mobile"))) %>% 
  ggplot(
    aes(
      x = Year, 
      y = value, 
      group = interaction(Type, Country)
    )
  ) +
  coord_cartesian(ylim = c(0, 1.00)) +
  scale_y_continuous(
    "Internet users (or subscriptions) / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  scale_x_date(
    breaks = breaks_width("5 years"),
    labels = label_date("'%y")
  ) +
  geom_line(size = .25, col = "dodgerblue4") +
  facet_grid(Type~Region) +
  theme(legend.position = "none")

p_itu
ggsave(
  "output/Fig-ITU.png", 
  device = agg_png,
  height = 2400, width = 3200, res = 300, units = "px"
)

p_itu %+% 
  (filter(p_itu$data, Type == "Internet") %>% 
     mutate(Region = str_replace(Region, "\n", " "))) + 
  scale_y_continuous(
    "Internet users / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  facet_wrap("Region", nrow = 2)
ggsave(
  "output/Fig-ITU-internet.png", 
  device = agg_png,
  height = 1200, width = 3200, res = 300, units = "px"
)
```

@@

```{r}
d_young <- d %>% 
  drop_na(Region) %>% 
  filter(Age %in% c("10 to 14", "15 to 19", "20 to 24"))

pa <- d_young %>% 
  ggplot(aes(Year, val, group = Country, col = Region)) +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .4) +
  facet_grid(Cause~Region, scales = "free_y") +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  )
pb <- d_young %>% 
  ggplot(aes(Year, val, col = Age, lty = Sex)) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .5) +
  facet_grid(Cause~Region, scales = "free_y")

@@

### GBD lm

Estimate OLS for each cause for country-sex-age specific estimates

```{r fit-gbd-time-lm}
file_path <- "output/lm-gbd-time.rds"
if (!file.exists(file_path)) {
  fits_lm <- d_young %>% 
    group_by(Cause) %>% 
    partition(cluster) %>% 
    summarise(
      fit = list(
        lm(
          val ~ 0 + Country:Sex:Age + Time:Country:Sex:Age,
          data = cur_data_all()
        )
      )
    ) %>% 
    collect() %>% 
    ungroup()
  write_rds(fits_lm, file_path)
} else {
  fits_lm <- read_rds(file_path)
}
```

```{r}
tidy(fits_lm$fit[[1]])
# Get country-sex-age specific parameters
fits_lm %>% 
  mutate(out = map(fit, tidy))
```

### GBD lme4

```{r fit-gbd-time-lmer}
# Fit GBD time lmer models
file_path <- "output/lme-gbd-time.rds"
if (!file.exists(file_path)) {
  fits_lme <- d_young %>% 
    group_by(Cause) %>% 
    partition(cluster) %>% 
    summarise(
      fit = list(
        lmer(
          val ~ 0 + Sex:Age + Time:Sex:Age + 
            (0 + Sex:Age + Time:Sex:Age | Region) +
            (0 + Sex:Age + Time:Sex:Age | Country),
          data = cur_data_all()
        )
      )
    ) %>% 
    collect() %>% 
    ungroup()
  write_rds(fits_lme, file_path)
} else {
  fits_lme <- read_rds(file_path)
}
```

```{r}
# lmer parameters
```

We want to visualise cluster-specific coefficients, but this is hard with lme4. Attempt

```{r}
# Get country-, region-, and age-specific parameters

# Create scatterplots
```

### GBD brms

Shall we fit multiple times: First without interaction with age, gender, then see if those matter?

```{r fit-gbd-time-brms}
fit_empty <- brm(
  val ~ 0 + Sex:Age + Time:Sex:Age + 
    (0 + Sex:Age + Time:Sex:Age | Country) +
    (0 + Sex:Age + Time:Sex:Age | Region),
  data = filter(d_young, Cause == "Depression"),
  file = "output/brm-gbd-time-empty",
  chains = 0,
  threads = 3,
)

fits_brm <- d_young %>% 
  group_by(Cause) %>% 
  summarise(
    fit = list(
      update(
        fit_empty,
        newdata = cur_data_all(),
        chains = 4,
        cores = 4,
        iter = 1600,
        warmup = 800,
        refresh = 10,
        threads = 3,
        file = str_glue("output/brm-gbd-time-{cur_group()}")
      )
    )
  ) %>%
  ungroup()
```

Fixed effects

>>>>

---
title: "Online analysis supplement"
description: |
  A global study of adolescents’ digital technology adoption and its associations with well-being and mental health
author:
  - name: Matti Vuorre
    url: https://vuorre.netlify.app
    affiliation: Oxford Internet Institute
    affiliation_url: https://www.oii.ox.ac.uk/people/matti-vuorre/
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
    fig_width: 8
    fig_height: 6
    fig_retina: 2
    dev: "ragg_png"
    code_folding: true
editor_options: 
  chunk_output_type: console
---

@@

It is written in R Markdown and therefore contains all the code required for reproducing our computations. However some parts of the code were parallelised to work best with our local setup, so having e.g. a different number of cores will significantly impact the run-time of this script.

Therefore we recommend reproducing the analyses by running them in interactive mode, and changing the parallelisation parameters by hand to best fit your setup.

@@

```{r packages-settings}
#| results: 'hide'
# Packages
library(readxl)
library(ggtext)
library(janitor)
library(brms)
library(gtsummary)
library(imputeTS)
library(broom.mixed)
library(ragg)
library(scales)
library(ggh4x)
library(tidybayes)
library(naniar)
library(ggdist)
library(parameters)
library(countrycode)
library(lme4)
library(emmeans)
library(plotly)
library(knitr)
library(patchwork)
library(bayestestR)
library(lubridate)
library(haven)
library(janitor)
library(broom)
library(kableExtra)
library(ggbeeswarm)
library(ggstance)
library(sysfonts)
library(tidyverse)

@@

@@

We downloaded the relevant data from sources to `data-raw/`. We cannot share the data here but indicate below how and when each data table was obtained.

### Global Burden of Disease

The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/gbd-2021-11-02/`. We selected the relevant locations, age groups, years, and causes from the data tool as detailed in the manuscript. Next we load all tables (inside downloaded `.zip` files, there may be more than one depending on size of downloaded table) inside the directory.

```{r gbd-data-load}
# Load data files and merge to one table
gbd <- list.files(
  "data-raw/GBD/gbd-2021-11-02/", 
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>% 
  read_csv()
```

We then ensure that the correct variables were downloaded, and then clean this data.

```{r gbd-data-clean}
# Cleaning

# First step is to clean names in all data sets
gbd <- clean_names(gbd)

# Confirm that correct measures were downloaded:
# - prevalence: Total number of cases
# - rate: Total cases per 100,000 population
#   - We convert this to a percentage
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>% 
  mutate(across(c(val, upper, lower), ~.x/1000))

# Clean cause names
# distinct(gbd, cause)
gbd <- gbd %>% 
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Selfharm"
    )
  )

# Harmonise variable names with other datasets
gbd <- gbd %>% 
  rename(country = location)

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions).We convert those to normal approximate standard errors.
gbd <- gbd %>% 
  mutate(se = (upper-lower) / (1.96*2)) %>%
  select(-c(upper, lower))
```

Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`. There is a harmonised name for each GBD country, and 27 country names are harmonised.

```{r gbd-harmonise-countries}
# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>% 
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>% 
  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")
# Harmonise old names after verifying above that none are dropped
gbd <- gbd %>% 
  mutate(country = countryname(country, destination = "cldr.short.en"))
```

### Gallup World Poll

GWP cleaning goes here.

### International Telecommunication Union

The internet adoption data were downloaded from the ITU website in October 2021, and placed with their original file names to `data-raw/ITU/`. The specific URLs for obtaining the data files are

@@

We first load, reshape, and merge these datasets.

```{r itu-load-clean}
# Read and reshape fixed broadband data
itu_fixed <- read_xlsx(
  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(fixed = as.numeric(value)) %>% 
  select(country = Country, year, fixed)

# Read and reshape mobile broadband data
itu_mobile <- read_xlsx(
  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(mobile = as.numeric(value)) %>% 
  select(country = Country, year, mobile)

# Percent using internet
itu_percent <- read_xlsx(
  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(internet = as.numeric(value)) %>% 
  select(country = Country, year, internet)

# Merge to one table in wide format (oldest on left to include all years)
itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)

# values (1-100) to proportions (0-1) and years to numbers
itu <- itu %>% 
  mutate(across(c(internet, fixed, mobile), function(x) x/100)) %>% 
  mutate(year = as.numeric(year))

@@

Then harmonise country names as above, and drop countries that don't exist in outcomes.

```{r itu-harmonise-countries}
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>% 
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>% 
  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

# Harmonise old names after verifying above that none are dropped
itu <- itu %>% 
  mutate(country = countryname(country, destination = "cldr.short.en"))

# These countries don't exist in outcomes
itu %>%
  distinct(country) %>% 
  anti_join(distinct(gbd, country)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

# Drop them
itu <- itu %>% 
  filter(country %in% unique(gbd$country))
```

#### Missingness

Remove countries with no observations

```{r}
itu <- itu %>% 
  group_by(country) %>% 
  mutate(nobs = sum(!is.na(internet))) %>% 
  ungroup() %>% 
  filter(nobs > 0) %>% 
  select(-nobs)
```

There are some missing values in the data; in the Internet variable these are mainly in the first or last years of each country's time-series. This needs to be changed to calculate by-variable (with appropriate time-spans) when adding mobile and fixed

```{r}
miss_var_summary(itu)
```

We then impute missing values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values.

```{r itu-impute}
itu <- itu %>% 
  group_by(country) %>% 
  # Find first and last year with internet data in each country
  mutate(
    min_year = year[min(which(!is.na(internet)))],
    max_year = year[max(which(!is.na(internet)))]
  ) %>%
  # Interpolate values linearly
  # use possibly() to avoid errors for countries with no data
  # Add variables to c() to impute for fixed and mobile broadband
  mutate(
    across(
      c(internet), 
      possibly(
        function(x) na_interpolation(x, maxgap = Inf), 
        # If function errors, provide original internet value
        otherwise = internet
      )
    )
  ) %>% 
  # Take out projected (non-intermediate) imputed values
  mutate(
    internet = if_else(
      between(year, unique(min_year), unique(max_year)), 
      internet, 
      NaN
    )
  ) %>% 
  ungroup() %>% 
  select(-min_year, -max_year)
```

We see that 96 intermediate internet use values were imputed to the time series.

```{r}
miss_var_summary(itu)
```

### Complete study dataset

#### GLOBE regions

We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised. This allows us to eg. present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models. We use the extended GLOBE regions following Jebb et al. (2020), and had to manually add labels to some countries that were not grouped in those studies.

```{r}
regions <- read_csv(
  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
) %>% 
  # Jebb et al used * to indicate deviance from GLOBE, remove
  mutate(country = str_remove_all(country, "\\*")) %>% 
  # Standardize country names
  # This drops Nagorno-Karabakh Republic
  mutate(country = countryname(country)) %>% 
  drop_na(country)

# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
regions <- distinct(regions, region, country)

# Countries in our dataset not present in region data
filter(
  distinct(gbd, country), 
  !(country %in% unique(regions$country))
) %>% 
  arrange(country) %>% 
  write_csv("data-raw/Regions/GBD-countries-without-region.csv")

# I then filled missing regions in Jebb et al and extended GLOBE referenced therein

# Load our manually filled region data
regions_filled <- read_csv(
  "data-raw/Regions/GBD-countries-without-region-filled.csv"
) 
```

We then combine all the region tables, clean region names, and join to our data

```{r}
# Combine Jebb et al GLOBE regions and our manually added ones
regions <- regions %>% 
  bind_rows(
    regions_filled %>% 
      mutate(Note = "Filled")
  ) %>% 
  arrange(region, country)

# Shorter name for plots
regions <- regions %>% 
  mutate(region = if_else(region=="Sub-Sahara Africa", "Africa", region))

# Format regions to factors and use line breaks instead of spaces
regions$region <- factor(regions$region)
levels(regions$region) <- str_replace_all(levels(regions$region), " ", "\n")

# Display table of regions and countries
regions %>% 
  kbl(caption = "All countries and regions.") %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

regions <- select(regions, -Note)
```

#### Create predictors

We then create predictors (centered, lagged, rescaled) for models in the ITU dataset.

```{r}
# For models, we rescale year; centred at 2013 and one unit indicates decade
itu <- itu %>% 
  mutate(time = (year - 2013) / 10)

# Create predictor: Lagged effect of 10% increase in internet
itu <- itu %>% 
  arrange(country, year) %>% 
  group_by(country) %>% 
  mutate(i1 = lag(internet*10, 1)) %>% 
  ungroup()

# Centering within and between countries
itu <- itu %>%
  bmlm::isolate("i1", by = "country", which = "both")
```

#### Create tables

Here, we join the ITU table to the GBD table. Note this appropriately duplicates the country-specific predictor values to the demographic groups within each country. We then create a table specific to young people.

We also join regions to the data.

```{r}
# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)

# Merge data tables
gbd <- left_join(gbd, itu)

# Contrast code sex
gbd$sex <- factor(gbd$sex)
contrasts(gbd$sex) <- c(-.5, .5)

# Focus on young people
gbd_all <- gbd
gbd <- gbd %>% 
  filter(age %in% c("15 to 19", "20 to 24"))

# Contrast code binary age in young data set
gbd$age <- factor(gbd$age)
contrasts(gbd$age) <- c(-.5, .5)

# Young data in wide format
gbd_wide <- gbd %>%
  pivot_wider(names_from = cause, values_from = c(val, se))
names(gbd_wide) <- str_remove(names(gbd_wide), "val_")
```

@@

```{r}
itu %>% 
  filter(year %in% c(2001, 2019)) %>% 
  select(region, country, year, internet) %>% 
  pivot_wider(names_from = year, values_from = internet) %>% 
  select(-country) %>% 
  tbl_summary(by = region) %>% 
  add_overall()
itu %>% 
  group_by(country) %>% 
  summarise(x = sum(!is.na(internet))) %>% 
  arrange(x)
```

```{r}
# Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
itu %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(x = year, y = internet, group = country)) +
  coord_cartesian(ylim = c(0, 1.00)) +
  scale_y_continuous(
    "Internet users / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  scale_x_date(
    breaks = breaks_width("5 years"),
    labels = label_date("'%y")
  ) +
  geom_line(size = .25, col = "dodgerblue4") +
  facet_wrap(~region, nrow = 2) +
  theme(legend.position = "none")
ggsave(
  "output/Fig-ITU.png", 
  device = agg_png,
  height = 1400, width = 3200, res = 300, units = "px"
)
```

@@

```{r}
pa <- gbd %>% 
  ggplot(aes(year, val, group = country, col = region)) +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .5) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  )
pb <- gbd %>% 
  mutate(Group = str_glue("{sex} ({age})")) %>% 
  ggplot(aes(year, val, col = Group)) +
  scale_color_brewer(palette = "Paired") +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    "Year",
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .6) +
  facet_grid(cause~region, scales = "free_y")

@@

We first fit the models using lme4 because they are big and therefore would be very slow with brms.

#### lme4

```{r fit-gbd-time-lme4}
# These take about 5-20 minutes each
# run in parallel in background jobs
# recommended to conduct this in interactive mode (rstudio)
file_path <- "output/lme4-gbd-time.rds"
if (!file.exists(file_path)) {
  library(job)
  job({fit_anx <- lmer(
    Anxiety ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Anxiety time (lmer)")
  job({fit_dep <- lmer(
    Depression ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Depression time (lmer)")
  job({fit_sel <- lmer(
    Selfharm ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Self harm time (lmer)")
  fits_lmer <- distinct(gbd, cause) %>% 
    mutate(fit = list(fit_anx, fit_dep, fit_sel))
  write_rds(fits_lmer, file_path)
} else {fits_lmer <- read_rds(file_path)}
```

Plot fixed effects and by demographic

```{r}
# Fixed effects parameters
fixed_effects <- fits_lmer %>% 
  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  filter(
    Effects == "fixed", 
    Parameter != "(Intercept)"
  ) 
# Fixed effects per demographic
fixed_effects_demographics <- fits_lmer %>% 
  mutate(
    out = map(
      fit,
      ~emtrends(.x, var = "time", by = c("sex", "age")) %>% 
        parameters() %>% 
        as.data.frame()
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  mutate(Parameter = str_glue("{sex}\n({age})"))

# Random effects parameters
random_effects <- fits_lmer %>% 
  mutate(
    coef_region = map(
      fit, 
      ~bind_rows(
        coef(.x)$region %>% 
        as.data.frame() %>% 
        rownames_to_column("region"),
        coef(.x)$country %>% 
        as.data.frame() %>% 
        rownames_to_column("country"),
        .id = "cluster"
      ) %>% 
        mutate(cluster = factor(cluster, labels = c("region", "country")))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(coef_region) %>% 
  mutate(Type = "Effects") %>%
  select(-`(Int      ,nc ercept)`)

# Calculate random demographics time effects
random_effects %>% 
  mutate(
    `Male (20 to 24)` = time + `time:sex1`*.5 + `time:sex1:age1`*.25
  )

pivot_longer(
    c(`(Intercept)`:`time:sex1:age1`, `Male (20 to 24)`:`Female (15 to 19)`), 
    names_to = "Parameter", 
    values_to = "Coefficient"
    )
